Poster_Plots

### 2022-11-14 Poster_plots.Rmd
add plots update legends

Theme_special<-function()
{
  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
        axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
        strip.text = element_text(colour = "black",size = 12,face="bold"),
        panel.grid.minor.x = element_blank(),
        axis.title= element_text(color = "black",face = "bold",size = 12),
        legend.text = element_text(color = "black", size=11),
        legend.position = "bottom",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-1,-2,-1,-2)) 
}

>>>>

Theme_special<-function()
{
  theme(axis.text.x = element_text(color = "black",size=18, angle = 45, hjust=0.75), #, vjust = 0.5
        axis.text.y = element_text(color = "black",size=18), #, vjust = 0.5, hjust=1
        strip.text = element_text(colour = "black",size = 16,face="bold"),
        panel.grid.minor.x = element_blank(),
        axis.title= element_text(color = "black",face = "bold",size = 15),
        legend.text = element_text(color = "black", size=12),
        legend.position = "bottom",
        #legend.margin=margin(1,3,1,3),
        #legend.box.margin=margin(1,3,1,3)
        legend.key.width=unit(0.05,"npc"),
        legend.margin = margin(), # pre-emptively set zero margins
        legend.spacing.x = unit(0.2, "cm")) 
}
